### 2024-06-07 thesis/input_files/paper1.tex
fixed typo

$$ 
\begin{aligned}
    \mathcal{F} =\bigg\{ \sum\limits_{i=1}^n \alpha_i k(x_i, \cdot): n \in \mathbb{N}, x_i, y_i \in \mathcal{X}, a_i \in \mathbb{R}, i=1,\cdots, n \bigg\}    
\end{aligned}
$$
This space is clearly closed under addition of functions and scalar multiplication. Therefore, it is a vector space.
Letting $f(x)=\sum\limits_{i=1}^n \alpha_i k_i(x_i,x)$ and $g(x)=\sum\limits_{i=1}^m \beta_i k_i(y_i,x)$,  we can introduce an inner product on $\mathcal{F}$ as

$$
\begin{aligned}
    \langle f,g \rangle_{\mathcal{F}}:=\sum\limits_{i=1}^n\sum\limits_{j=1}^m a_i \beta_j k_i(x_i,y_j)=\sum\limits_{i=1}^n a_i g(x_i)= \sum\limits_{j=1}^m \beta_j f(y_j)
\end{aligned}
$$

>>>>

$$ 
\begin{aligned}
    \mathcal{F} =\bigg\{ \sum\limits_{i=1}^n \alpha_i k(x_i, \cdot): n \in \mathbb{N}, x_i, y_i \in \mathcal{X}, a_i \in \mathbb{R}, i=1,\cdots, n \bigg\}    
\end{aligned}
$$
This space is clearly closed under addition of functions and scalar multiplication. Therefore, it is a vector space.
Letting $f(x)=\sum\limits_{i=1}^n \alpha_i k(x_i,x)$ and $g(x)=\sum\limits_{i=1}^m \beta_i k(y_i,x)$,  we can introduce an inner product on $\mathcal{F}$ as

$$
\begin{aligned}
    \langle f,g \rangle_{\mathcal{F}}:=\sum\limits_{i=1}^n\sum\limits_{j=1}^m a_i \beta_j k(x_i,y_j)=\sum\limits_{i=1}^n a_i g(x_i)= \sum\limits_{j=1}^m \beta_j f(y_j)
\end{aligned}
$$
